---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(badger)
library(knitr)
library(mutatomic)
set.seed(1)
```

# mutatomic

<!-- badges: start -->
`r badge_repostatus("WIP")`
`r badge_lifecycle("experimental")`
`r badge_custom("ORCID", "0000-0001-9498-8379", "green",   "https://orcid.org/0000-0001-9498-8379")`
<!-- badges: end -->



mutatomic: Tools for Safe Pass-by-Reference Modification Semantics on Atomic Objects

## Description

Provides tools, including a new class ('mutatomic'), for safe pass-by-reference modification semantics on atomic objects. Primary purpose for this package is so the 'mutatomic' class and its related tools are accessible for other packages that wish to implement safe pass-by-reference semantics for atomic objects.

&nbsp;

## Get Started

To get started see `?mutatomic_help` or click `here`.

&nbsp;

## Installing & Loading

One can install 'mutatomic' from GitHub like so:

```{r eval = FALSE, echo = TRUE}
remotes::install_github("https://github.com/tony-aw/mutatomic")
```

One can attach the package - thus exposing its functions to the namespace - using:

```{r eval = FALSE, echo = TRUE}
library(mutatomic)
```

&nbsp;
